\documentclass[margin,line]{resume}
\usepackage[hidelinks]{hyperref}

\begin{document}
\name{\Large Samuel Brotherton}
\begin{resume}
    \section{\mysidestyle Contact\\Information}

    Phone: (801) 927-0219       \hfill LinkedIn: \url{https://www.linkedin.com/in/sbrother} \\
    \noindent Email: sbrother@gmail.com  \hfill Address: 7771 Buckboard Drive, Park City, UT 84098 \vspace{0mm}\\\vspace{-4.5mm}

    \section{\mysidestyle Education}

    \textbf{Harvard University}, Cambridge, MA \vspace{2mm}\\\vspace{1mm}%
    \textsl{B.A., Mathematics and East Asian Studies} \hfill \textbf{Sep 2008 -- May 2012}\\
    Received highest honors for senior thesis analyzing over 200,000 Chinese
    blog posts, algorithmically detecting mutations in the Chinese language in
    response to censorship. Completed coursework in abstract algebra,
    Galois theory, topology, real and complex analysis, probability theory, and
    linguistics.

    \section{\mysidestyle Professional\\Experience}

    \textbf{Cairn Labs}, Los Angeles, CA / Portland, OR / Park City, UT \vspace{2mm}\\\vspace{1mm}%
    \textsl{Founder \& Principal} \hfill \textbf{Jan 2016 -- Feb 2021, Jun 2025 -- Present}\\
    Founded a successful boutique consultancy to design and build software
    for clients, with a focus on applications that integrate state-of-the-art
    AI and machine learning. Managed a team of 2-18 depending on clients' needs.
    Most projects involve a multi-year timespan including the sales, design, and
    implementation phases, followed by eventual transition to in-house
    resources. Our clients have cumulatively raised over \$500M of venture
    funding using our prototyping and fractional CTO services. A small selection
    of notable projects includes:

    \begin{itemize}

    \item \textbf{i.am+}: Led a team of {\raise.17ex\hbox{$\scriptstyle\sim$}}20
      developers (a mix of in-house in Los Angeles and outsourced resources in
      India and Singapore) building a deep learning based conversational UI
      framework to power will.i.am's wireless earphones and other applications.
      Backed by Tensorflow, Prolog, and other technologies. Supported multiple
      languages, extensible dialogue flows, and a custom knowledge base. We
      eventually licensed the software to Deutsche Telecom, where it powered the
      Tier 1 Customer Service chatbot in Germany. See \url{https://goo.gl/iMvVTt}.

    \item \textbf{Authentic Artists}: Led a remote engineering team to build AI-powered audiovisual
      experiences, including a cloud deep learning server for song generation, a
      C++ constraint/transformation library for imposing additional musical style
      on its output, and an automated Max/Ableton session for audio generation.
      Coordinated with creative and executive teams to balance engineering and IP
      development with artistic and business goals. See
      \url{https://open.spotify.com/album/4ws0VXLBCNhk7tL033xfD5} for examples.

    \item \textbf{Live Circle}: Served as fractional CTO at a Healthcare AI
      startup over the course of seven years. Managed in-house and contract
      resources to build a voice-first care management platform to connect
      patients, caregivers, and clinical staff. Authored several patents and
      journal articles; see \textsc{Selected Publications} for examples.

    \item \textbf{Blue Cross Blue Shield}: Designed and delivered a highly
      available, HIPAA-compliant machine learning inference server used to
      predict asthma risk in real time from claims records.

    \end{itemize}

    \textbf{Reddit}, San Francisco, CA / Park City, UT (Remote)  \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer, Machine Learning} \hfill \textbf{Mar 2024 -- Jun 2025}\\
    Joined the Ads Engineering team shortly before IPO as a Machine Learning Engineer.
    Rolled out a new platform for optimizing ad group budget within the bidding
    and pacing team, using Scala and Akka Streaming. Designed and implemented a
    prototype Ad Targeting AI tool (using an agentic LLM backend) to help
    advertisers and AEs quickly build optimal campaigns. Led development of
    several new data driven recommendation modules to push advertisers toward
    higher and more effective spend.

    \textbf{Nextdoor}, San Francisco, CA / Park City, UT (Remote)  \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer} \hfill \textbf{Jan 2023 -- Mar 2024}\\
    Tech lead on a team building a next generation advertisement platform from
    scratch while gradually migrating Nextdoor's existing
    {\raise.17ex\hbox{$\scriptstyle\sim$}}\$250M of revenue off of a legacy
    platform powered by Google Ads Manager. Extensive cloud infrastructure
    development to introduce, maintain, and monitor streaming and batch data
    pipelines using Apache Beam in Kotlin, Flink, Kafka, and TimescaleDB on
    Kubernetes/AWS.

    \textbf{Google}, Los Angeles, CA / Park City, UT (Remote)  \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer} \hfill \textbf{Jun 2014 -- Mar 2016, Feb 2021 -- Jan 2023}\\
    Two stints as a software engineer within Google Display Ads:

    \begin{itemize}
    \item Early career, I worked on a small team using natural language
      processing and other machine learning techniques to improve advertisement
      quality. Led a 20\% project related to mining semantic information from
      web data, which was adopted by several teams across different product
      areas. Built a named entity recognition system in C++ and a link detection
      algorithm that runs on very large graphs; contributed to a topic model for
      clustering semantic entities.

    \item Boomeranged five years later under Google's COVID-era remote work
      policy, joining as a software engineer on an infrastructure team within
      Ads Privacy and Security using natural language processing and machine
      learning to prevent policy-violating ad impressions. Our systems handled
      2M+ queries per second and combined modern deep learning techniques with
      multi-tier human evaluation pipelines. Additionally, I had a 20\% role
      building remote sensing infrastructure and machine learning models for a
      stealth climate ``startup'' within Google.

    \end{itemize}

    \textbf{Whisper}, Venice, CA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer and Data Scientist} \hfill \textbf{Mar 2013 -- Apr 2014}\\
    Sole data scientist at a rapidly expanding social media startup
    seeing upwards of three billion monthly pageviews. Designed and built an NLP
    service to extract topics and tags from posts, predict image searchterms
    from unstructured text, and target content to users. Implemented a new
    geographic search system using PostGIS that decreased search time by
    90\%. Worked closely with the front and backend development teams, writing
    production code in Erlang and Python.

    \section{\mysidestyle Selected\\Publications}
    Brotherton, T., Brotherton, S., Ashworth, H., Kadambi, A., Ebrahim, H. and Ebrahim, S., 2022. Development of an Offline, Open-Source, Electronic Health Record System for Refugee Care. \emph{Frontiers in Digital Health}, 4.

    Demiris, G., Oliver, D.P., Washington, K.T., Chadwick, C., Voigt, J.D., Brotherton, S. and Naylor, M.D., 2022. Examining spoken words and acoustic features of therapy sessions to understand family caregivers’ anxiety and quality of life. \emph{International Journal of Medical Informatics}, 160, p.104716.

    Demiris, G., Corey Magan, K.L., Parker Oliver, D., Washington, K.T., Chadwick, C., Voigt, J.D., Brotherton, S. and Naylor, M.D., 2020. Spoken words as biomarkers: using machine learning to gain insight into communication as a predictor of anxiety. \emph{Journal of the American Medical Informatics Association}, 27(6), pp.929-933.

    Stephens, M., Bensink, M., Brotherton, S., Chandler, D., Garcia, J. and Hollenbeak, C., 2016. Geographic Access to Oncology Services in the United States (US): Travel Disparities May Affect Granulocyte-Colony Stimulating Factor (G-CSF) Administration. \emph{Blood}, 128(22), p.5905.

    Stephens, M., Brotherton, S., Dunning, S., Emerson, L., Gilbertson, D., Harrison, D.J., Kochevar, J., McClellan, A., McClellan, W., Wan, S. and Gitlin, M., 2011. The End-stage Renal Disease (ESRD) Prospective Payment System (PPS) and Access to Care: Incremental Distance Traveled by Displaced Patients.

\section{\mysidestyle Programming\\Experience}

\emph{Languages:} Python, Kotlin, C++, Erlang, Elixir, Scala, Golang, Mathematica,  C\#, F\#,
Bash, C, \LaTeX \\
\emph{Server Technology:} Kubernetes, Docker, GCP, AWS, Azure, Cassandra, Redis,
PostgreSQL, ElasticSearch, Apache Beam, Apache Flink, TimescaleDB, Akka Streaming,
Helm, Terraform, Neo4J, Dagster

\end{resume}
\end{document}
